Supplement to ``{\mytitle}''

### 2023-01-17 ms.Rnw
names, addresses

\author[A]{\fnms{Jesse}~\snm{Wheeler}\ead[label=e1]{jeswheel@umich.edu}\orcid{0000-0003-3941-3884}},
\author[A]{\fnms{AnnaElaine}~\snm{Rosengart}\ead[label=e2]{aelr@umich.edu}}
\author[A]{\fnms{Zhuoxun}~\snm{Jiang}\ead[label=e3]{zhuoxunj@umich.edu}},
\author[A]{\fnms{Kevin}~\snm{Hao En Tan}\ead[label=e4]{kevtan@umich.edu}},
\author[A]{\fnms{Noah}~\snm{Treutle}\ead[label=e5]{ntreutle@umich.edu}}
\and
\author[A]{\fnms{Edward}~\snm{Ionides}\ead[label=e6]{ionides@umich.edu}}

\address[A]{Statistics Department, University of Michigan\printead[presep={,\ }]{e1,e2,e3,e4,e5,e6}}

@@

We implemented this model using the \code{spatPomp} \code{R} package \citep{asfaw22cran}.
The model was then fit using the subplex algorithm, implemented in the  \code{subplex} package \citep{king2020Subplex}.
A comparison of the trajectory of the fitted model to the data is given in Fig~\ref{fig:mod2Traj}.

>>>>

\author[A]{\fnms{Jesse}~\snm{Wheeler}\ead[label=e1]{jeswheel@umich.edu}\orcid{0000-0003-3941-3884}},
\author[B]{\fnms{AnnaElaine L.}~\snm{Rosengart}\ead[label=e2]{arosenga@andrew.cmu.edu}}
\author[A]{\fnms{Zhuoxun}~\snm{Jiang}\ead[label=e3]{zhuoxunj@umich.edu}},
\author[A]{\fnms{Kevin}~\snm{Tan}\ead[label=e4]{kevtan@umich.edu}},
\author[A]{\fnms{Noah}~\snm{Treutle}\ead[label=e5]{ntreutle@umich.edu}}
\and
\author[A]{\fnms{Edward L.}~\snm{Ionides}\ead[label=e6]{ionides@umich.edu}}

\address[A]{Statistics Department, University of Michigan\printead[presep={,\ }]{e1,e3,e4,e5,e6}}

\address[B]{Statistics \& Data Science Department, Carnegie Mellon University\printead[presep={,\ }]{e2}}

@@

We implemented this model using the \code{spatPomp} \code{R} package \citep{asfaw23arxiv}.
The model was then fit using the subplex algorithm, implemented in the  \code{subplex} package \citep{king2020Subplex}.
A comparison of the trajectory of the fitted model to the data is given in Fig~\ref{fig:mod2Traj}.

### 2023-01-17 si/si.Rnw
version ready for circulating
names, addresses

\date{\today}
\title{Supplement to ``{\mytitle}''}
  \author{Jesse Wheeler, Anna Rosengart, Zhuoxun Jiang, \\ Kevin Hao En Tan, Noah Treutle, Edward L. Ionides
 \\ \hspace{.2cm}\\
    Department of Statistics, University of Michigan\\
}

@@

The source code that the Model~2 authors used to generate their results was written in the \code{Python} programming language, and is publicly available at \url{10.5281/zenodo.3360857} and its accompanying GitHub repository \url{https://github.com/lulelita/HaitiCholeraMultiModelingProject}.
In order to perform our analysis in a unified framework, we re-implemented this model in the \code{R} programming language using the \code{spatPomp} package \citep{asfaw22cran}, which facilitates the creation of meta-population models.
We note that the travel and water matrices used to implement the complex dynamics in Model~2 \citep{lee20sup} are not available in either the Zenodo archive or the GitHub repository;
instead, we obtained these matrices via personal correspondence with the Model~2 authors.
Using these matrices, and the point estimates for model parameters provided by \citep{lee20sup}, we created trajectories of the cholera dynamics and compared this to available data.
These trajectories, shown in Figure~\ref{fig:mod2rep}, are very similar to the trajectories shown in Figure~S15 of \cite{lee20sup}.

>>>>

\date{\today}
\title{Supplement to ``{\mytitle}''}
  \author{Jesse Wheeler, AnnaElaine L. Rosengart, Zhuoxun Jiang, \\ Kevin Tan, Noah Treutle and Edward L. Ionides
 \\ \hspace{.2cm}\\
    Department of Statistics, University of Michigan\\
}

@@

The source code that the Model~2 authors used to generate their results was written in the \code{Python} programming language, and is publicly available at \url{10.5281/zenodo.3360857} and its accompanying GitHub repository \url{https://github.com/lulelita/HaitiCholeraMultiModelingProject}.
In order to perform our analysis in a unified framework, we re-implemented this model in the \code{R} programming language using the \code{spatPomp} package \citep{asfaw23arxiv}, which facilitates the creation of meta-population models.
We note that the travel and water matrices used to implement the complex dynamics in Model~2 \citep{lee20sup} are not available in either the Zenodo archive or the GitHub repository;
instead, we obtained these matrices via personal correspondence with the Model~2 authors.
Using these matrices, and the point estimates for model parameters provided by \citep{lee20sup}, we created trajectories of the cholera dynamics and compared this to available data.
These trajectories, shown in Figure~\ref{fig:mod2rep}, are very similar to the trajectories shown in Figure~S15 of \cite{lee20sup}.
